Enforcing Boundaries: China's Overseas NGO Law and Operational Constraints for Global Civil Society

### 2024-02-27 manuscript/manuscript.qmd
More in theory section + some initial modeling caveats

The right half of @fig-theory illustrates alternative determinants of INGO operational space that lie outside of organizations' potential contentiousness or relationships with the government. An INGO's preferences---that is, its strategy, mission, and goals---also influence how much operational space is available in host countries. For instance, many INGOs have missions focused on local issues and communities---they work on specific projects with naturally limited scopes and have no need to expand their work. The nature of an organization's programming also influences its reach and flexibility: a human rights advocacy organization interested in holding a national government accountable for civil liberties abuses will have a much broader geographic and political scope---and thus require greater operational flexibility---than an education organization interested in supporting a handful of primary schools. An INGO's available resources also determine its in-country flexibility. An organization with more funding, more employees, more connections with local regulators or politicians, or other types of resources can benefit from additional flexibility when working in its host country by, for instance, enjoying greater geographic access, more leeway in adherence to regulations, or a wider menu of possible strategies available to accomplish its mission. Organizations with fewer resources, on the other hand, will have more limited operational space. These organization-level determinants can be seen as independent of government preferences

To test the relationships between government preferences, INGO issue area, INGO characteristics, and operational space, we apply this conceptual model to China's 2017 ONGO law. Previous research has looked at *A posteriori* (notes: I don't know if it is a correct use of latin words, I want to say how the INGO sector is like in a timeframe after the law) effects of civil society laws on a global scale [@LianMurdie:2023; @Chaudhry:2022], which naturally blurs the specific policy mechanisms regimes use for controlling and leveraging global civil society. By analyzing the population of formally registered INGOs between 2017–2021, we can more precisely explore how a single formal restrictive INGO law has shaped the operational space for foreign organizations working in the country. Specifically, we can observe exactly how the Chinese government has used the RO registration process to strategically limit and reshape these organizations' operational space. We conducted both a descriptive analysis of the composition of the issue areas of INGOs successfully registered under the INGO law and a regression analysis of the relationship between INGO issue areas and their operational space.

@@

> **E~2~**: Because they are explicitly focused on local issues, INGOs with explicitly local missions should be registered in fewer provinces.

We also took into account the temporal factor, the time elapsed since the law took effect when the ROs got registered. Since there was a *de facto* grace period for INGOs to seek registration even though theoretically all existing INGOs should obtain the legal status right after January 1, 2017, the timing of registration for ROs varies by years. More time elapsed since the enforcement of the law can mean INGOs took more efforts to seek an ideal registration results, and they are more rest-assured to maintain a not-yet-legal status because they do not work in contentious issue areas. For example, World Animal Protection has been wording in China since 2007, but they did not register their office until two years after the ONGO Law took effect.

@@

>>>>

The right half of @fig-theory illustrates alternative determinants of INGO operational space that lie outside of organizations' potential contentiousness or relationships with the government. An INGO's preferences---that is, its strategy, mission, and goals---also influence how much operational space is available in host countries. For instance, many INGOs have missions focused on local issues and communities---they work on specific projects with naturally limited scopes and have no need to expand their work. The nature of an organization's programming also influences its reach and flexibility: a human rights advocacy organization interested in holding a national government accountable for civil liberties abuses will have a much broader geographic and political scope---and thus require greater operational flexibility---than an education organization interested in supporting a handful of primary schools. An INGO's available resources also determine its in-country operational space. These organization-level determinants are independent of host government preferences and represent possible resources an INGO can draw on based on the laxity or strictness of the *de facto* enforcement of civil society laws in a country. An organization with more funding, more employees, more connections with local regulators or politicians, or other types of resources can benefit from additional flexibility when working in its host country by, for instance, enjoying greater geographic access, more leeway in adherence to regulations, or a wider menu of possible strategies available to accomplish its mission. Organizations with fewer resources, on the other hand, will have more limited operational space.

To test the relationships between government preferences, INGO issue area, INGO characteristics, and operational space, we apply this conceptual model to China's 2017 ONGO law. China provides a unique case for exploring these different mechanisms. The implementation and enforcement of the law has been quite strict, and since government data regarding INGOs is complete, we are able to observe the entire population of INGOs granted RO status since 2017. By analyzing all formally registered INGOs between 2017--2021, we can more precisely explore how a single formal restrictive civil society law has shaped the operational space for foreign organizations working in the country. Government data about each INGO provides each organization's issue area, mission, and scope, and by looking at each organization's geographic reach and registration timeline, we can get a sense of organization-level operational flexibility. Importantly, by modeling and exploring the composition of permitted INGOs, we can observe exactly how the Chinese government has used the RO registration process to strategically limit and reshape these organizations' operational space.

@@

> **E~2~**: Because they are focused on local issues, INGOs with explicitly local missions should be registered in fewer provinces.

Finally, TODO We also took into account the temporal factor, the time elapsed since the law took effect when the ROs got registered. Since there was a *de facto* grace period for INGOs to seek registration even though theoretically all existing INGOs should obtain the legal status right after January 1, 2017, the timing of registration for ROs varies by years. More time elapsed since the enforcement of the law can mean INGOs took more efforts to seek an ideal registration results, and they are more rest-assured to maintain a not-yet-legal status because they do not work in contentious issue areas. For example, World Animal Protection has been working in China since 2007, but they did not register their office until two years after the ONGO Law took effect.

@@

We are not interested in statistical significance or hypothesis testing. Instead, we are interested in the overall registration patterns across our three expectations. Accordingly, while we report full model coefficients, care should be taken to not be concerned if those coefficients are statistically different from zero, or if coefficients for one issue area are statistically different from another issue area. Instead, we use these model results to generate posterior predictions that illustrate the full range of possible registration patterns.

This is also apparent in our graphical results. Rather than display coefficients that demonstrate the marginal effects of one issue area compared to another, we provide posterior predictions of the expected counts and proportions of authorized provinces. The model results are thus descriptive explorations of our expectations, not confirmatory hypothesis tests.
